Probabilistic Catalogs for Crowded Stellar Fields

### 2012-10-30 paper/ms.tex
Captions

\begin{figure}
\begin{center}
\includegraphics[scale=0.33]{Figures/inference1.eps}
\end{center}
\caption{Inference about the parameters for test case 1.\label{fig:results1}}
\end{figure}

\subsection{Test Case 2}

\begin{figure}
\begin{center}
\includegraphics[scale=0.33]{Figures/inference2.eps}
\end{center}
\caption{Inference about the parameters for test case 2.\label{fig:results2}}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=0.33]{Figures/inference1.eps}
\end{center}
\caption{Inference about the parameters for Test Case 1. Note that there is
considerable uncertainty (particularly about $h_2$), which occurs because the
shape of the broken power-law does not depend strongly on the parameters.
\label{fig:results1}}
\end{figure}

\subsection{Test Case 2}
Test Case 2 is more challenging than Test Case 1 because the image contains
more stars. This increases the size of the computational task in a number of
ways: firstly, there will be more unknown parameters to infer, so the
convergence of the MCMC algorithm will take longer. Secondly, the time taken
to compute the predicted image from a catalog (in order to evaluate the
likelihood) is longer because of the larger number of stars.

\begin{figure}
\begin{center}
\includegraphics[scale=0.33]{Figures/inference2.eps}
\end{center}
\caption{Inference about the parameters for Test Case 2.\label{fig:results2}}
\end{figure}
